Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-09 paper.tex
Comments on nipype paragraph

\usepackage{hyperref}
\usepackage{xcolor}

\newcommand{\note}[1]{\textcolor{green}{\textit{note}: #1}}

\begin{document}
\title{Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data}
\author{Valerie Hayot-Sasson}
\maketitle
\begin{abstract}
  Text of abstract.  
\end{abstract}
\tableofcontents
\chapter{Introduction}
intro here
\chapter{BigData and Open science in neuroimaging}
    \note{Likely will not be split in two separate sections}
    \section{large images}
        \begin{itemize}  
            \item BigBrain
            \item Micro CT 
            \item EM 
        \end{itemize}
    \section{large datasets}
    	\note{off the top of my head, but need to double check}
        \begin{itemize}
            \item HCP
            \item ADNI
            \item OpenFMRI
            \item BIDS/BIDS apps
        \end{itemize}
    An effective engine to process such data requires the following characteristics
        \begin{itemize}
            \item in-memory computing
            \item data locality
            \item lazy evaluation
        \end{itemize}
        \section{open-science /data sharing platforms for neuroimaging}
        		is open science just data sharing, computing. 
        		\subsection{Introduction}
		\subsection{CBRAIN}
		\subsection{OpenNEURO}
		\subsection{NeuroData}
\chapter{Workflow engines for neuroimaging data}
	\section{Definition of workflows/pipelines}
	\section{Nipype}
		\subsection{summary}
		Nipype\cite{nipype} is a popular neuroimaging pipelinening framework written in python.
		It provides users with uniform access to the rich ecosystem of neuroimaging software
		libraries (e.g. SPM, FSL, Freesurfer) through its \textit{Interfaces}. Should users want to
		use their own custom tool, it is also possible to create an interface for that. To execute 
		python code in Nipype, the \textit{Function} interface can be used. The framework is 
		also easy to use, and thus does not contribute to the steep learning curve new
		researchers must face.

		A pipeline in Nipype, consists of a data analysis \textit{Workflow} of connected \textit{interfaces}. The workflow is a directed acyclic graph that connects the outputs of one interface to be the inputs of another. A workflow may also consist of connected workflows. Workflows may be executed in parallel either locally or an a cluster through the use of a plugin in the Workflow's run function. For debugging, Nipype uses \textit{graphiz} to generate a static graph representing the Nodes and their relationships.

		 Each \textit{interface} within the workflow must be contained within a \textit{Node} or a \textit{MapNode} object. The MapNode class being a subclass of the Node class. Wrapping an interface in such objects ensures that interfaces are executed within a uniquely named directories, which in turn enables provenance tracking. Node objects also hash inputs, provide the ability to iterate over inputs and cache results. Hash inputs are useful in the case of Workflow recomputation, where Nipype will only recompute Nodes whose inputs have changed since the previous run.

		Inspired by the mapreduce paradigm, the MapNode copies the interface to each input and executes it independently. A reduce is subsequently performed by the MapNode to return the output in the form of a list. This differs from a Node object which can only execute the interface on a single input at a time.

@@

		\subsection{limitations of nipype}
		Nipype, although meeting the various needs of researchers in Neuroinformatics, was not designed with the processing of Big Data in mind. Moreover, its performance relative to current Big Data frameworks remains unknown.
		\note{nipype performs a lot of disk I/O. Recomputation of workflows vs RDD caching}

>>>>

\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{ulem}

\newcommand{\note}[1]{\textcolor{green}{\textit{note}: #1}}
\newcommand{\tristan}[1]{\textcolor{red}{TG: #1}}
\newcommand{\weird}[1]{\uwave{#1}}

\begin{document}
\title{Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data}
\author{Valerie Hayot-Sasson}
\maketitle
\begin{abstract}
  Text of abstract.  
\end{abstract}
\tableofcontents
\chapter{Introduction}
intro here
\chapter{BigData and Open science in neuroimaging}
    \note{Likely will not be split in two separate sections}
    \section{large images}
        \begin{itemize}  
            \item BigBrain
            \item Micro CT 
            \item EM 
        \end{itemize}
    \section{large datasets}
    	\note{off the top of my head, but need to double check}
        \begin{itemize}
            \item HCP
            \item ADNI
            \item OpenFMRI
            \item BIDS/BIDS apps
        \end{itemize}
    An effective engine to process such data requires the following characteristics
        \begin{itemize}
            \item in-memory computing
            \item data locality
            \item lazy evaluation
        \end{itemize}
        \section{open-science /data sharing platforms for neuroimaging}
        		is open science just data sharing, computing. 
        		\subsection{Introduction}
		\subsection{CBRAIN}
		\subsection{OpenNEURO}
		\subsection{NeuroData}
\chapter{Workflow engines for neuroimaging data}
	\section{Definition of workflows/pipelines}
	\section{Nipype}
		\subsection{summary}
		Nipype\cite{nipype} is a popular neuroimaging pipelinening framework written in Python.
		It provides users with uniform access to the rich ecosystem of neuroimaging software
		libraries (e.g. SPM, FSL, Freesurfer) through its \textit{Interfaces}. \weird{Should users want to
		use their own custom tool, it is also possible to create an interface for that}. To execute 
		Python code in Nipype, the \textit{Function} interface can be used \tristan{for arbitrary code?}. The framework is 
		also easy to use, and thus does not contribute to the steep learning curve new
		researchers must face.

		A pipeline in Nipype, consists of a data analysis
                \textit{Workflow} of connected
                \textit{interfaces}. The workflow is a directed
                acyclic graph that connects the outputs of one
                interface to be the inputs of another. A workflow may
                also consist of connected workflows.

                \tristan{The text below is about workflow execution
                  while the text above is about workflow description,
                  this should be a new paragraph.}  Workflows may be
                executed in parallel either locally or an a cluster
                through the use of a plugin in the Workflow's run
                function. For debugging, Nipype uses \textit{graphviz}
                to generate a static graph representing the Nodes and
                their relationships. \tristan{debugging might be a
                  third theme, in addition to description and
                  execution. Provenance might go in debugging.}

		 Each \textit{interface} within the workflow must be
                 contained within a \textit{Node} or a
                 \textit{MapNode} object, the MapNode class being a
                 subclass of the Node class. Wrapping an interface in
                 such objects ensures that interfaces are executed
                 within a uniquely named directories, which in turn
                 enables provenance tracking. Node objects also hash
                 inputs, provide the ability to iterate over inputs
                 and cache results. Hash inputs are useful in the case
                 of Workflow recomputation, where Nipype will only
                 recompute Nodes whose inputs have changed since the
                 previous run.

		Inspired by the MapReduce paradigm, the MapNode copies
                the interface to each input and executes it
                independently. \tristan{How are inputs defined/combined?} A reduce is subsequently performed by
                the MapNode to return the output in the form of a
                list. This differs from a Node object which can only
                execute the interface on a single input at a time.

@@

		\subsection{Limitations}
		Nipype, although meeting the various needs of
                researchers in Neuroinformatics \tristan{vague}, was
                not designed with the processing of Big Data in
                mind. Moreover, its performance relative to current
                Big Data frameworks remains unknown \tristan{You could
                  refer to your MS thesis here}.  \note{nipype
                  performs a lot of disk I/O. Recomputation of
                  workflows vs RDD caching}
